Negative Types

### 2015-03-23 Univalence/outline.tex
added new file FinSetCategory to eventually replace CauchyEquiv

\paragraph*{FinEquiv.} Establishes that $\texttt{Fin}~n$ also forms a commutative semiring with $\simeq$ as the underlying equivalence relation. In particular, we have:
\[\begin{array}{rcll}
\texttt{Fin}~0 &\simeq& \bot \\
\texttt{Fin}~1 &\simeq& \top \\
\texttt{Fin}~(m+n) &\simeq& \texttt{Fin}~m \uplus \texttt{Fin}~n \\
\texttt{Fin}~(m*n) &\simeq& \texttt{Fin}~m \times \texttt{Fin}~n
\end{array}\]
and then we have all the commutative semiring axioms, e.g.,
$\texttt{Fin}~(0+m) \simeq \texttt{Fin}~m$.

\paragraph*{CauchyEquiv.}

>>>>

\paragraph*{FinEquiv.} Establishes that $\texttt{Fin}~n$ also forms a
commutative semiring with $\simeq$ as the underlying equivalence
relation. In particular, we have:
\[\begin{array}{rcll}
\texttt{Fin}~0 &\simeq& \bot \\
\texttt{Fin}~1 &\simeq& \top \\
\texttt{Fin}~(m+n) &\simeq& \texttt{Fin}~m \uplus \texttt{Fin}~n \\
\texttt{Fin}~(m*n) &\simeq& \texttt{Fin}~m \times \texttt{Fin}~n
\end{array}\]
and then we have all the commutative semiring axioms, e.g.,
$\texttt{Fin}~(0+m) \simeq \texttt{Fin}~m$. The actual proof says that
0, 1, $+$, and $*$ for a commutative semiring structure under the
equivalence that equates $m$ and $n$ if
$\texttt{Fin}~m \simeq \texttt{Fin}~n$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bimonoidal Categories}

\paragraph*{FinSetCategory.} Defines the category of finite sets and
all functions between them. As stated on the nLab page, ``it is easy
(and thus common) to make \texttt{FinSet} skeletal; there is one
object for each natural number $n$ (including $n=0$), and a morphism
from $m$ to $n$ is an $m$-tuple $(f_0,\ldots,f_{m−1})$ of numbers
satisfying $0 \leq f_i < n$. This amounts to identifying $n$ with the
set $\{0,\ldots,n−1\}$.'' This structure will be a building block for
permutations (defined in \texttt{ConcretePermutation}).
